Methods for Large Scale Learning to Rank

### 2014-04-14 report/Chapters/BenchmarkResults.tex
stuk bullshit verwijderd

Since LETOR is arguably the most well-known benchmark collection in the field, it is conceivable that creators of new Learning-to-Rank methods evaluate their new method on the LETOR collection to show how well their new method works. To create an overview of the performance of newer Learning-to-Rank methods on LETOR 3.0 we perform a forward reference search on the LETOR 3.0 paper \cite{Qin2010}. It should be noted that results of evaluations individually performed by the creator of the evaluated Learning-to-Rank method can not be regarded as equally reliable as the evaluations performed by the LETOR team. TODO: 307 citations, x evaluated a new Learning-to-Rank method on LETOR 3.0, x were usable. The unusable studies did test a new Learning-to-Rank method on one or more datasets of the LETOR collection, but 1 ) did not use a ranking metric used in LETOR (\ac{nDCG} or \ac{MAP}) or 2) did not list evaluation results at all.\\

>>>>

Since LETOR is arguably the most well-known benchmark collection in the field, it is conceivable that creators of new Learning-to-Rank methods evaluate their new method on the LETOR collection to show how well their new method works.
